\documentclass[12pt]{article}
%\usepackage{parskip}
\usepackage[margin=2in]{geometry}
\usepackage{ebgaramond}
\usepackage{microtype}
\title{The Star Gardeners}
\author{Finn Buck}
\begin{document}

\maketitle

%Buts and Ands shouldn't really start sentences unless they have to.
%We need to go through and edit the tense again.

Somewhere,
suspended in the silent starry void of spacetime,
the people of the earth lived out another twenty-first century Tuesday.
As dawn raced around the globe's girdle,
countless millions rose like marionettes
and explained their life's purpose to themselves in the groggy minutes of the morning between the alarm and getting dressed.
Headlines roared out from newspapers.
Trucks honked red lights back to green.
Bored fingers manipulated buttons, keyboards, and levers.
And content was created in multitudes---some of it with great care,
some of it entirely frivolously
and a lot of it seemingly accidentally.
All the same, it was created and then stored away,
lovingly arranged into ones and zeroes, to join a constantly swelling stream of data.

While it was certainly a thoroughly ordinary Tuesday on earth,
that particular span of twenty-four hours did, in fact, have somewhat more interesting ramifications for the galaxy as a whole.
This was because it was the first earth day of any kind silently witnessed by the Mithro-akoi---and thus they would be able to document the existence of humans for posterity.
For on that very day a starship piloted by two-dozen Mithro-akoi was gently gliding through our solar system in close proximity to our own cloud-enshrouded planet.
The crew had navigated it there on a type of mission that, unfortunately, has no simple analogue in any human society.
One could say they were good samaritan conquistadors,
or, perhaps, soul sailors on a stormy sea of cosmic empathy.
In their own language these travelers from afar referred to themselves simply as `star gardeners'.

The ship that these star gardeners had now steered into a languid orbit around the earth was a vast dome of asteroid-pocked metal.
It was a great chariot of meteoric iron that had been forged directly in outer space 
and had never suffered the indignity of becoming ensnared in any planet's atmosphere.
A trusty workhorse,
it had trod the dusty trails and nebulous swamps of the galaxy for eons uncounted.
The Mithro-akoi relied on the ship for protection from the ferocious cold of the cosmos and were safely encased deep within its metallic heart.
There,
submerged in inky black embalming fluids they lay quietly dreaming,
sustained by the warmth of a captive miniature star that served as the ship's engine.

Now,
in order to better comprehend the motives of these voyageurs,
it is important to have a basic understanding of the beliefs that make up the Mithro-akoi's own traditional cosmology.
At the heart of their belief system lies the conviction that their physical selves are, in fact, no more than three-dimensional shadows of transcended beings inhabiting much higher dimensions.
Their true selves, they thus firmly believe, dwell in an unfathomable spirit world that borders directly upon the reality in which we live.
Initiates into the Mithro-akoi mysteries claim to be able to venture into this spirit world in order to commune with their higher-dimensional selves and receive insights into the ways of the universe.
It is a strict requirement that four such initiates should always be present in any operating crew of star gardeners.

Thus the four initiates upon this starship had meticulously charted a zig-zagging route through the galaxy following their own mysterious principles.
At this particular moment they had been led to earth by a very peculiar belief that they had all nonetheless come to an incontrovertible consensus on.
The peculiar belief, roughly expressed, was that the humans of the earth were more or less identical to the Mithro-akoi on a spiritual level.
That is to say, they believed that humans were in fact no more than a different kind of shadow of the same higher dimensional beings that the Mithro-akoi held to be their true selves.
In an analogy to lower dimensions, one could see how a floating cylinder might have a circular shadow when illuminated from above and a rectangular shadow when illuminated from the side.
This, the Mithro-akoi initiates believed, fully accounted for the apparent physical differences between humans and Mithro-akoi---they were nothing else but the same kind of souls illuminated from different angles.

The extent to which the traditional beliefs of the Mithro-akoi hold merit as an accurate account of the universe remains controversial and is a question that galactic scholars will most likely still have to grapple with for centuries to come.
Highly peculiar, however, is the fact that they were able to use their spiritual techniques to predict the earth's position with an incredible precision.
Their final reckoning was off by but a handful of astronomical units and from that proximity the planet could easily be detected by conventional means.
The task of finding earth would certainly have been devilishly difficult for any other spacefaring civilization of their time, 
for the small rocky planet was, as of yet, hopelessly underdeveloped and had emitted almost no significant electromagnetic signals across any appreciable distances.

Locating such a small and sparsely-inhabited world in a region of the galaxy previously thought to be completely devoid of life would therefore have amounted to an astonishing technological breakthrough, 
but the Mithro-akoi took it for granted that revelations from the spirit world had shown them the direct path to their kindred souls.

Now that the starship had arrived at its destination, a low mechanical shudder started to shake its entire hull
accelerating slowly to become a steady and melodic hum.
One by one, the Mithro-akoi began to awaken,
floating gently in the womb-like darkness of their preservation pods.
Their fragile bodies were born aloft by thick fingers of warm black iron as the embalming fluid was drained away around them.
Soon their soft bulbous heads and glossy compound eyes were pushing upward through the dark mirror-like surface of their resting pools.
Implanted electrodes jolted their long-dormant lungs back into action with a shudder and dozens of metallic nourishing tubes snaked their way back out of the veins they had so long supplied.
The star gardeners began their first hours awake peacefully meditating on the purpose of their mission in the gloom of the main ship chamber.
Then they turned to the task at hand.

The first order of business was to begin processing the many faint electromagnetic signals emanating from the enigmatic blue planet before them.
To their delight, the Mithro-akoi soon found that their starship's exquisitely sensitive antennas were thrumming with a tremendous rush of activity.
Many of the received signals were already pre-processed conveniently into a system of ones and zeroes very similar to the one used by the Mithro-akoi themselves.
Within a few minutes, a working knowledge of all major human languages had been gained and the ship's computers had undertaken a routine evaluation of humanity's technological and scientific advancements.
Shining compound eyes reflected one hundred tiny versions of softly glowing numbers and graphs. 
Those Mithro-akoi tasked with planetary study and evaluation watched with great concentration.

Meanwhile, the presence of the starship went almost entirely unnoticed by human scientists.
Only the great white eye of a lazily circling hurricane looked back up at the star gardeners as they looked down from above.
Of course, here and there devices in research labs and military bases did register some anomalous patterns---it appeared there was a vague blip hovering just within the moon's orbit, 
seeming in all ways similar to a small asteroid. 
Peculiarly, however, the trajectory of this supposed asteroid could not be traced at all.
It was simply not there one moment and there the next.
Further investigation would have yielded still more troubling results
and perhaps roused the humans to suspicion, 
but, of course, by then the Mithro-akoi were already long gone.

While humanity remained blissfully unaware of its new audience,
a sense of consternation was already spreading on the Mithro-akoi ship.
It began to dawn on the star gardeners that,
based on their own aesthetic ideals,
humanity resembled more a thicket of weeds than a flowerbed.
Quite possibly, heavy pruning would soon be required if this corner of the galactic garden was to be kept in pristine shape.
Of course, any radical intervention would have to be preceded by a meticulous evaluation.
Clearly, the fate of the planet was a matter that would have to be brought before the four initiates.

A report was soon put together by the team of evaluators who sent it to the ship's central computing hub.
This titanic processing device consisted of a monolithic cube that was located within the private chamber of the Mithro-akoi initiates.
It formed the unofficial fifth member of the initiate council and had existed since long before any of the other council members had been born.
Around this gently glowing thinking-machine the Mithro-akoi initiates were presently gathered, ready to begin receiving the report and discussing its contents.
Before commencing, however, each initiate carefully hooked themselves into their personal drip-feeder.
These delicate silvery devices were designed to transport various chemical mixtures directly into the brains of the initiates through a port surgically implanted into their fleshy heads.

The procession of cerebrally administered substances had long been enshrined in the mystical doctrine of the Mithro-akoi.
It was now carefully followed.
To begin, a gentle stream of stimulants and focusing agents was sluiced into the initiate's brain matter.
This facilitated perfect poise and attention as the contents of the report on earth were read out by the computer.
Once heard, word upon word was flawlessly committed to memory.
No sooner had the reading finished,
than the drip-feeders began to flush out the stimulants with a more calming admixture.
The initiates then began to chant back the contents of the report several times, listening carefully to ensure that every member had received the same information.

As usual, no corrections were necessary and the initiates now focused on clearing their minds in anticipation of the next stage.
In this third stage, after reading and error-checking, 
the minds of the initiates were invaded by high doses of potent psychedelics.
Soon their thoughts began to loop and swirl, connecting disparate concepts and finding many strange and unlikely solutions.
This colorful conflagration of ideas was allowed to continue for a short time,
before a new set of chemicals was pumped through the brain-port in order to reign it in.
A chemical known to induce dangerous levels of paranoia in high doses was now added in trace amounts in order to facilitate the throwing out of bad ideas.

Being gradually brought out of the psychedelic delirium,
the initiates spent much of the fourth stage running simulations on the computing hub in order to ascertain which of their high-flying ideas were the most viable.
As of yet, they remained in complete silence as each worked in solitude in order to prepare their best arguments.
The exchange of ideas would wait until the next stage of the process.

For in the fifth stage each Mithro-akoi initiate was hit with a virulent dose of amphetamines and morale-raising hormones.
Silence was quickly eschewed in favor of ever more strident advocacy on behalf of each of the four different solutions that the initiates had arrived at.
The central processing hub made vague attempts to keep things civil by interjecting at times,
but the arguments soon turned bitter and heated,
fueled by the frenzy inducing cocktail of drugs.

Just as the dispute reached a fever-pitch,
the mixture was flushed out and replaced once again.
In the sixth and final stage, 
chemical empathy and peace was flooded into the frenzied minds of the initiates.
Then, as words of conflict suddenly clattered to the floor, the combative mood in the room was replaced by a dawning sense of understanding.
Soon, the initiates began to trade sheepish apologies across the room, 
and they began to grasp each other's views perfectly.
While they had spent the past few minutes heatedly clarifying and defending their ideas they had now gained the emotional capacity to understand what each of the others had been saying all along. 
With this new-found harmony it became easy to combine their ideas constructively and to thus forge their final solution from aspects of each of their views.

Thus the ritual was complete and the fate of humanity had been decided.
The Mithro-akoi initiates proposed that out of every thousand humans all but one should be pruned by means of a taylor made virus.
This biblical flood in viral form was to make short work of human civilization 
and the survivors stood no chance of burying the countless dead. 
The clock was completely reset on the little progress that humanity had hitherto made,
but among the ruins the star gardeners hoped to find a thoroughly pruned and malleable human species that would be able to grow up to great beauty under their guidance.
In this way it was that the Mithro-akoi came to adopt us humans as their own and raise us to maturity.
Under their tutelage our species was finally able to join the greater community of our galaxy.





\end{document}